---
title: "Tutorial for CGED-Q"
---
#0. Preparation:准备阶段
1. Download the package:下载所需要的包(package)
```{r Download the package:}
install.packages("rgdal") #Geospatial' Data Abstraction Library
install.packages("sf") #Simple Features for R
install.packages("rgeos") #Interface to Geometry Engine - Open Source 
install.packages("sp")  #Classes and Methods for Spatial Data
install.packages("raster") #Geographic Data Analysis and Modeling
install.packages("glue") #Interpreted String Literals
install.packages("dplyr") #A Grammar of Data Manipulation

install.packages("tmap")
install.packages("tmaptools")
install.packages("OpenStreetMap")

install.packages("ggplot2")
install.packages("ggmap")

install.packages("leaflet")
```

2.Import the library导入

```{r  Import the library}
library(rgdal)
library(sf)
library(rgeos)
library(sp)
library(raster)
library(glue)
library(dplyr)

library(tmap)
library(tmaptools)
library(OpenStreetMap)

library(ggplot2)
library(ggmap)
```

Testing Chinese:
```{r Testing Chinese}
Sys.setlocale(locale = "us")

x <- "中文" # if get random thing here, need to change text encoding to utf-8
Encoding(x) <- "UTF-8"
Encoding(x)
```

#1. LOAD POLYGON FILE 导入地理Polygon信息
```{r load polygon file}
# read the shp file:
cnt <- (readOGR(dsn = "./v6_1911_cnty_pgn_utf/v6_1911_cnty_pgn_utf.shp",
                stringsAsFactors=FALSE))
```

Change the encoding and correct the type 整理编码信息，修改每一列的数据种类
```{r correct the type for each column}
#1-1 ENCODING AND CORRECT TYPE:
col_names = colnames(cnt@data)

#*****change character encoding to UTF-8******:
for (col in colnames(cnt@data)){
  if (class(cnt@data[[col]]) == "character"){
    Encoding(cnt@data[[col]]) <- "UTF-8"
    cnt@data[[col]]<- iconv(cnt@data[[col]], from = "UTF-8", to = "Latin1")
    Encoding(cnt@data[[col]]) <- "UTF-8"
  }
}

#factor:

for (col in (c("LEV_RANK", "BEG_RULE", "END_RULE", "DYN_PY", "BEG_YR","END_YR",
               "DYN_CH","LEV1_PY","LEV1_CH","LEV2_PY","LEV2_CH","OBJ_TYPE","COMPILER","GEOCOMP","TYPE_PY", "TYPE_CH"))){
  cnt@data[[col]] <- as.factor(cnt@data[[col]])
}

#change some number to correct number type:
for (col in c("SYS_ID", "OID_", "NOTE_ID", "SYS_ID_1","X_COORD","Y_COORD")){
  print(col)
  cnt@data[[col]] <- as.numeric(cnt@data[[col]])
}

#check col name and type again:
sapply(cnt@data, class)

#modify the cnt to show only 2 characters:
cnt$NAME_FT <- substr(cnt$NAME_FT,1,2)

cnt_name = levels(as.factor(cnt$NAME_FT))

#rm unwanted variables:
rm(col)
```

#2. LOAD CGED-Q FILE 导入CGED-Q 信息

```{r Load CGED-Q file}
# header = FALSE to encode colname as well
jsl <- read.csv("./CGED-Q/CGED-Q+Public+Release+1900-1912+9+May+2019.csv",header = TRUE, stringsAsFactors = TRUE, encoding = "UTF-8")
#get col name:
jsl_cp <- read.csv("./CGED-Q/CGED-Q+Public+Release+1900-1912+9+May+2019.csv",header = FALSE, stringsAsFactors = FALSE, encoding = "UTF-8", nrows = 1)

colnames(jsl) <- jsl_cp[1, ] # the first row will be the header
colnames(jsl)[1] <- "阳历年份" #fix some strange bug
rm(jsl_cp)

#change jsl to correct datatype:
#factor_additional:

for (col in c("阳历年份", "季节号", "插补号", "卷号", "册号")){
  jsl[[col]] <- as.factor(jsl[[col]])
}

#character_additional:
jsl[["姓"]] <- as.character(jsl[["姓"]])
jsl[["名"]] <- as.character(jsl[["名"]])
jsl[["字号"]] <- as.character(jsl[["字号"]])

#FINISH
```


整理CGED-Q的数据
```{r match the name from jsl to cnt}

#Start matching the county name

#clean the data
#1. remove cnt which is NA
jsl <- jsl[jsl["籍贯县"] != "",]
#2. remove cnt which has unrecognized name:
jsl <- jsl[!(jsl[["籍贯县"]] %in% (grep("？", levels(as.factor(as.character(jsl[["籍贯县"]]))), value = TRUE))),]

#3. change typo, ex: "甯" to "寧"
jsl[["籍贯县"]] <- gsub("甯","寧",jsl[["籍贯县"]])
jsl[["籍贯县"]] <- gsub("寗","寧",jsl[["籍贯县"]])
jsl[["籍贯县"]] <- gsub("寕","寧",jsl[["籍贯县"]])

jsl[["籍贯县"]] <- gsub(" ","",jsl[["籍贯县"]])

#4. keep only the first 2 characters
jsl[["籍贯县"]] <- substr(jsl[["籍贯县"]], 1, 2)

#5. check which county is not in cnt_name
jsl_name_unshow_in_cnt <- jsl[!(jsl[["籍贯县"]] %in% cnt$NAME_FT),][["籍贯县"]]
jsl_name_unshow_in_cnt <- levels(as.factor(jsl_name_unshow_in_cnt))

# Here we only keep the counties which appeared both in cnt and jsl
jsl <- jsl[!(jsl[["籍贯县"]] %in% jsl_name_unshow_in_cnt),]
```


#3. PREPARE THE ATTRIBUTE YOU WANT TO VISUALIZE 准备需要可视化的信息
```{r prepare the ranking for each county}
# need to summarize what you want to show from jsl, and then join into cnt polygon 
jsl_sel <- jsl[(jsl[["阳历年份"]]== 1911) & (! is.na(jsl[["阳历年份"]])) & (jsl[["出版单位"]] == "") ,]
people_ag <-as.data.frame(table(unlist(jsl_sel[["籍贯县"]])))
colnames(people_ag) <- c("籍贯县","FREQUENCY")

people_ag <- people_ag[order(people_ag$FREQUENCY),]
rownames(people_ag) <- NULL
people_ag$rank <- dense_rank(people_ag$FREQUENCY)

# Show the first two rows of the aggregated data
head(people_ag, 2)

head(cnt$NAME_FT) # dataset to add to (results not shown)
head(people_ag$"籍贯县") # the variables to join
```


```{r Join two tables}
#the `left_join` function from the **dplyr** package but the `merge` function
#could equally be used. 
head(left_join(cnt@data, people_ag, by = c('NAME_FT' = '籍贯县'))) # test it works
#We use left_join because we want the length of the data frame to remain unchanged
cnt@data <- left_join(cnt@data, people_ag, by = c('NAME_FT' = '籍贯县'))
```
```{r}
#***NEW** get correct boundary box
b_cnt <- bbox(cnt)
b_cnt[2,1] <- 1000000

#If you want basemap:
#To create a basemap with tmap, you can use the `read_osm` function, 
#from the [**tmaptools** package](https://github.com/mtennekes/tmaptools) as follows. 
#Note that you must first transform the data into wgs
cnt_wgs <- spTransform(cnt, CRS("+init=epsg:4326"))
b <- bbox(cnt_wgs)
b[2,1] <- 4 #enlarge the longitude

```

#(Alternative) 4. PLOT USING BASIC PLOT FUNCTION 用基本的函数画地图
```{r 4-0 whole picture}
#WHOLE PICTURE
plot(cnt)
#draft try, testing on cnt shp data
```

```{r 4-1: plot the first 5 counties in the list:}
#4-1: plot the first 5 counties in the list:
sel <- head(cnt, n = 5)
plot(sel)

#highlight the first county to blue:
sel <- head(cnt, n = 1)
plot(sel, add = T, col = "lightblue")
```

```{r 4-2: print selected name county:}
#4-2: print selected name county:
sel <- cnt[cnt$NAME_FT == "懷柔",]
plot(sel, col = "lightblue") 
```

```{r 4-3 plot subplaces around one place:}
#4-3:1 plot subplaces around one place:
sel <- cnt[cnt$NAME_FT == "懷柔",]
cent_cnt <- gCentroid(cnt[sel,]) 
points(cent_lnd, cex = 3)

#4-3:2 set 10 km buffer, get a buffer from point cent_lnd
cnt_buffer <- gBuffer(spgeom = cent_cnt, width = 50000) 

#4-3:3 subsetting selects any intersecting zones - light blue
cnt_central <- cnt[cnt_buffer,] # the selection is too big!
# test the selection for the previous method - uncomment below
plot(cnt_central, col = "lightblue")
plot(sel, add = T, col = "lightyellow") # highlight the selected area

#4-4: plot acoording to Area condition
cnt_area <- gArea(cnt,byid = TRUE) #calculate every counties area
sel <- cnt[cnt_area > 1e+10,]
plot(sel)
```


#5. PLOT USING DIFFERENT PACKAGES 用不同用户包画地图
#5-1: tmap package
Which you've been imported before

library(tmap)
library(tmaptools)
library(OpenStreetMap)

```{r 5-1-1:qtm: Quick thematic map plot}
#5-1-1:qtm: Quick Thematic Map
qtm(cnt, fill = "rank", bbox = b_cnt) # plot the basic map
```


```{r 5-1-2: changing the color}
#5-1-2
#more examples for basic usage of tmap:
#inverted the color scheme, deeper color means less frequency:
# The sequential palettes names are Blues BuGn BuPu GnBu Greens Greys Oranges OrRd PuBu PuBuGn PuRd Purples RdPu Reds YlGn YlGnBu YlOrBr YlOrRd
# The diverging palettes are BrBG PiYG PRGn PuOr RdBu RdGy RdYlBu RdYlGn Spectral And also cool_warm. 
qtm(shp = cnt, fill = "rank", fill.palette = "YlGn", bbox = b_cnt)
```


```{r 5-1-3: Using seperate functions to realize the same visualization:}
#5-1-3: Using seperate functions to realize the same visualization:
#it's equal to qtm(cnt, fill = "rank")
tm_img <- tm_shape(cnt, bbox = b_cnt) +
  tm_fill("rank", style = "cont" ,n = 10, thres.poly = 0) +
  tm_borders(col = "grey80", lwd = 0.5)
tm_img
#check the color cheatsheet for the color you want

tmap_save(tm = tm_img, filename = "../../Time_series/5-1-3.png")
```


```{r 5-1-4(X):If you want to add basemap:}
#5-1-4:If you want basemap:
#To create a basemap with tmap, you can use the `read_osm` function, 
#from the [**tmaptools** package](https://github.com/mtennekes/tmaptools) as follows. 
#Note that you must first transform the data into wgs
#***07/20/2019: it seemed we cannot use read_osm in China
osm_tiles <- read_osm(b)# read basemap from OpenStreetMap

#method1, static map: 
tmap_mode("plot")
tm_img <- tm_shape(osm_tiles, bbox = b) +
  tm_raster() +
  tm_shape(cnt_wgs) +
  tm_fill("rank", fill.title = "1911 Ranking of Each County", style = "cont" ,n = 10, scale = 1, alpha = 0.6)

tmap_save(tm = tm_img, filename = "../Time_series/5-1-4.png")
```


```{r 5-1-4:method2: with view mode}
#method2:
#By changing map mode, tmap_mode("view"), this will make the maps appear on a zoomable webmap powered by leaflet. 
#check demo source maps from http://leaflet-extras.github.io/leaflet-providers/preview/
tmap_mode("view")
  tm_basemap(bbox(cnt_wgs),server = "Esri.NatGeoWorldMap") +
  tm_shape(cnt_wgs) +
  tm_fill("rank", style = "cont" ,n = 10, scale = 1, alpha = 0.6)
```
#5-2: ggplot package
```{r 5-2-1:plot points using ggplot:}
#5-2-1:plot points using ggplot:
p <- ggplot(cnt_wgs@data, aes(X_COORD,Y_COORD))+
  ylim(10,NA) #enlarge the longitude
#The real power of ggplot2 lies in its ability to add layers to a plot. In this case we can add text to the plot.
#***ggplot2 cannot directly plot spatial object
p + geom_point(aes(colour = -`rank`))
```

ggplot cannot directly plot spatial object, so we need transfer it to dataframe

```{r 5-2-2: plot polygon using ggplot: preparation}
#5-2-2-1: preparation
# whether you want to only plot the selected part: sel = cnt[cnt$`rank` < 200 & !(is.na(cnt$`rank`)),]
cnt_f <- broom::tidy(cnt_wgs)#(after this step, cnt_f only contains polygon informaiton, it doesnt have other data information, so need to use left join from dplyr to join back the data information

head(cnt_f, n = 2) # peak at the fortified data
cnt_wgs$id <- row.names(cnt_wgs) # allocate an id variable to the sp data
head(cnt_wgs@data, n = 2) # final check before join (requires shared variable name)
cnt_f <- left_join(cnt_f, cnt_wgs@data) # join the data
```


```{r 5-2-2: plot polygon using ggplot:}
#create the ggplot (as we mentioned before, ggplot cannot directly plot spatial object.)
#long, lat are new col generated by tidy function
#Now we can use ggplot to plot polygon information
#**group = id is important
map <- ggplot(cnt_f, aes(long, lat, group = id, fill =`rank`)) +
  geom_polygon() + coord_equal() +
  labs(x = "X_COORD", y = "Y_COORD") +
  ggtitle("rank") +
  ylim(10,NA) #enlarge the longitude

#plot the map
map + scale_fill_gradient(low = "white", high = "red")
ggsave("../../Time_series/5-2-2.png", device = "png", scale = 5)
```



```{r}
#use ggmap for basemap:
# download map data for the lnd data and plot, there are three map source: google, openstreetmap,stamenmap.
#Since OpenStreetMap doesn't support get_map anymore, if you don't have google API, you can choose get_stamenmap
#as well as choosing maptype:
map <- ggmap(get_stamenmap(b, zoom = 7, maptype = "toner-lite"))  
```


```{r use ggmap for basemap:}
#plot the map:
map + 
  geom_polygon(data = cnt_f, aes(x = long, y = lat, group = id, fill = `rank`), alpha = 0.6) +
  scale_fill_gradient(low = "lightyellow", high = "red")

ggsave("../../Time_series/5-2-3.png", device = "png", scale = 5)
```


#6 MORE ATTEMPT: PLOT JIANSHENG INFORMATION 可视化监生的来源分布
```{r}

jsl_sel_2 <- jsl_sel[jsl_sel[["出身一"]]== "監生",]
people_ag <-as.data.frame(table(unlist(jsl_sel_2[["籍贯县"]])))
colnames(people_ag) <- c("籍贯县","jiansheng")

people_ag <- people_ag[order(people_ag$jiansheng),]
rownames(people_ag) <- NULL
people_ag$js <- dense_rank(people_ag$jiansheng)

# Show the first two rows of the aggregated data
head(people_ag, 2)

head(cnt$NAME_FT) # dataset to add to (results not shown)
head(people_ag$"籍贯县") # the variables to join
```


```{r Join two tables}
#the `left_join` function from the **dplyr** package but the `merge` function
#could equally be used. 
head(left_join(cnt_wgs@data, people_ag, by = c('NAME_FT' = '籍贯县'))) # test it works
#We use left_join because we want the length of the data frame to remain unchanged
cnt_wgs@data <- left_join(cnt_wgs@data, people_ag, by = c('NAME_FT' = '籍贯县'))
```

```{r}
#method1, static map: 
tmap_mode("plot")
tm_img <- tm_shape(osm_tiles) +
  tm_raster() +
  tm_shape(cnt_wgs) +
  tm_fill("js", style = "cont" ,n = 10, scale = 1, alpha = 0.6)

tmap_save(tm = tm_img, filename = "../../Time_series/6.png")
  
```

